Hydra Battles and Cie

### 2021-09-06 doc/chapter-primrec.tex
corrections chapters 8,9

\begin{Coqanswer}
3 subgoals (ID 184)

  ============================
  isPR 1 (fun _ : nat => 2)

subgoal 2 (ID 185) is:
 isPR 1 (fun x : nat => x)
subgoal 3 (ID 186) is:
 isPR 2 Init.Nat.mul
\end{Coqanswer}

@@

\input{movies/snippets/isqrt/boundedSearch3}
\input{movies/snippets/isqrt/boundedSearch4}

@@

\begin{Coqanswer}
 x : PrimRec m
 x0 : nat
 H : forall v : t nat n,
   max_v (map (fun f : naryFunc n => v_apply f v)
           (evalPrimRecs n m g)) <=
   Ack x0 (max_v v)
 x1 : nat
 H0 : forall v : t nat m, v_apply (evalPrimRec m x) v <=
                                  Ack x1 (max_v v)
  ============================
  forall v : t nat n,
  v_apply (evalPrimRec n (composeFunc n m g x)) v <=
  Ack (2 + Nat.max x0 x1) (max_v v)

\end{Coqanswer}

@@

\begin{Coqanswer}
  n : nat
  x1 : PrimRec n
  x2 : PrimRec (S (S n))
  r : nat
  Hg : forall v : t nat n,
     v_apply (evalPrimRec n x1) v <= Ack r (max_v v)
  s : nat
  Hh : forall v : t nat (S (S n)),
       v_apply (evalPrimRec (S (S n)) x2) v <= Ack s (max_v v)
  ============================
  majorizedPR (primRecFunc n x1 x2) Ack
\end{Coqanswer}

The las two goals deal with vectors of functions.

\begin{Coqanswer}
1 subgoal (ID 289)

  n : nat
  ============================
  majorizedSPR (PRnil n) Ack

\end{Coqanswer}

\begin{Coqanswer}
1 subgoal (ID 296)

  n, m : nat
  x : PrimRec n
  p : PrimRecs n m
  IHx : majorizedPR x Ack
  IHx0 : majorizedSPR p Ack
  ============================
  majorizedSPR (PRcons n m x p) Ack
\end{Coqanswer}

\begin{Coqsrc}
Qed.
\end{Coqsrc}

>>>>

@@

\inputsnippets{isqrt/boundedSearch3, isqrt/boundedSearch4}

@@

@@

The last two goals deal with vectors of functions.

\input{movies/snippets/AckNotPR/majorAnyPRVec}
